Estimating Fixed Frame Galaxy Magnitudes in the SDSS$^1$

### 2002-09-04 docs/paper/paper.tex
all
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@148 75dff457-8751-0410-ab1a-cd701654ce6b

We want to emphasize here that, while $K$-correcting to a fixed frame
bandpass is {\it sometimes} necessary in order to achieve a scientific
objective, it is not {\it always} necessary or appropriate. Because
$K$-corrections are inherently uncertain (the broad band magnitudes
do not uniquely determine the SED) they should be avoided or
minimized when possible. For example, if one were calculating the
evolution of clustering of red and blue galaxies separately, it would
perhaps be wise to perform the separation not on the $K$-corrected
colors of the galaxies but on the median color of $M_\ast$
galaxies as a function of redshift. Similarly, in situations where
$K$-corrections cannot be ignored, such as the calculation of the
evolution of the luminosity function, their effect should be minimized
by, for example, correcting to the median redshift of galaxies in the
sample.

>>>>

We want to emphasize here that, while $K$-correcting to a fixed frame
bandpass is {\it sometimes} necessary in order to achieve a scientific
objective, it is not {\it always} necessary or appropriate. Because
$K$-corrections are inherently uncertain (the broad band magnitudes do
not uniquely determine the SED) they should be avoided or minimized
when possible. For example, if one were calculating the evolution of
clustering of red and blue galaxies separately, it would perhaps be
wise to perform the separation not on the $K$-corrected colors of the
galaxies but on the median color of $M_\ast$ galaxies as a function of
redshift. Similarly, in situations where $K$-corrections cannot be
ignored, such as the calculation of the evolution of the luminosity
function, their effect should be minimized by, for example, correcting
to a band shifted to the median redshift of galaxies in the sample.
